Dusty galaxies and the degeneracy between their dust distributions and the attenuation formula

### 2015-04-14 response.txt

* Still on the vocabulary, I do not think it is defined anywhere what
"dust-poor" and "dusty" galaxies are. This sort of thing contributes to
the vagueness of the paper. The reader does not know what she is really
looking it. A more quantitative description of the two samples would be
especially useful. Directly related to this point, another important
issue I have is the very unclear selection of the sample. I do not think
the reader would understand why these sample specifically were selected.

We clarify our language in the last paragraph on the Introduction.  The
sample of low-redshift dust-poor galaxies is included to show that we
can reproduce the Calzetti result; the samples of dusty galaxies are
included because we know little about their dust distributions.

* "We often assume that dust grains are distributed as a uniformly thick
screen between us and the galaxy's stars and gas (Calzetti et al.
1994).". I do not see where Calzetti would have stated that. What they
say in the abstract is "The data from the 39 galaxies are compared with
five models for the geometrical distribution of dust, adopting as
extinction laws both the Milky Way and the Large Magellanic Cloud laws.
The commonly used uniform dust screen is included among the models. We
find that none of the five models is in satisfactory agreement with the
models". What the authors perhaps mean is that 20 years ago some people
still considered an uniform dust screen as an acceptable model. I think
this time is long gone, even though it is sometimes referred to as a
standard comparison point as it has a very simple link with the optical
depth.

The abstract has a small fraction of the content of the paper. Calzetti
et al. 1994 has an extended discussion of the uniform screen model in
sections 5.1 and 6.2.  We clarify our discussion of the uniform screen
model in the Introduction.

@@

* "An attenuation formula is denoted k(lambda) or k'(lambda)." I do not
think this statement is useful here. First the term "attenuation
formula" is extremely vague. Then, unless I am mistaken, k is not used
in any meaningful way elsewhere in the paper anyway.

* "A low-redshift galaxy [...] underestimates the measured Halpha
attenuation." Please back this with a reference.

* "Liu+13 find that the dust distribution around ionizing stars
throughout M83 is clumpy at a spatial scale of 6 pc." Unless I am
mistaken, this is not at all what they say. Quoting their abstract
"[...] we conclude that a large diversity of absorber/emitter geometric
configurations can account for the data, implying a more complex
physical structure than the classical foreground screen assumption". The
article barely mentions at all the clumpy distribution.

We clarify our summary of their conclusions.  The abstract has a small
fraction of the content of the paper.  The clumpy distributions are
discussed in detail in section 3.2.

@@

* "If we choose to think of dust distributions as clumpy [...] 60% of
the number of clumps surrounding ionizing stars (Calzetti+97a)". Once
again, I do not see where the mentioned paper cites that number. If it
is indeed that paper: http://de.arxiv.org/abs/astro-ph/9706121 then the
word clump is not even mentioned even once in the paper. Please clarify
this part.

The referee has an incorrect link.  The paper we cite is: Calzetti, D.
1997, AJ, 113, 162.

### 2015-04-14 paper.tex
Better summary of Liu results

The screen part of our assumption is suspect, but it may be a
good approximation to the truth.  The
screen assumption is qualitatively similar to a scenario in which dust is
distributed in a large number of clumps \citep{calzetti94}.  \citet{liu13} find
that the dust
distribution around ionizing stars throughout M83 is clumpy at a spatial scale
of 6 pc;
if the spatial resolution is degraded to 100 pc, we conclude that the
distribution around ionizing stars is a screen.  If we choose to think of dust
distributions as clumpy, the number of clumps surrounding nonionizing
UV-emitting stars in low-redshift dust-poor galaxies is 60\% of the number of
clumps surrounding ionizing stars \citep{calzetti97a}.

>>>>

The screen part of our assumption is suspect, but it may be a
good approximation to the truth---the alternative assumption being that dust
mixes with stars.  \citet{liu13} study the dust distribution of M83 at a
spatial scale of 6 pc.  They divide M83 into a center and outskirts.  For each
part, they calculate the percentage of regions with ionizing stars mixed with
dust.  Only in the center does this percentage exceed 50.  If they degrade the
spatial resolution to 100 pc, they conclude that the dust distribution around
ionizing stars is a screen.  The screen assumption is qualitatively similar to
a scenario in which dust is distributed in a large number of clumps
\citep{calzetti94}.  If we choose to think of dust distributions as clumpy, the
number of clumps surrounding nonionizing UV-emitting stars in low-redshift
dust-poor galaxies is 60\% of the number of clumps surrounding ionizing stars
\citep{calzetti97a}.
